Reducing Acceptance Marks in Emerson-Lei Automata by QBF-solving

### 2022-03-03 paper/main.tex
smal changes in structure of the paper

\paragraph*{Structure of the paper} The next section introduces basic
terms used in the paper. Section~\ref{sec:qbf} explains the
construction of three mentioned QBF formulas. The reduction algorithm
based on these formulas is described together with its implementation
in Section~\ref{sec:algimpl}. Section~\ref{sec:experiments} shows the
experimental results. Finally, Section~\ref{sec:conclusion} suggests
other applications of our QBF-based reduction technique and closes the
paper.

@@

%}}}
%{{{ algorithm and implementation

\section{Reduction algorithm and its implementation}\label{sec:algimpl}
Jak se nastavuji inicialni parametry a jak postupne klesaji.
Jak prechazim od nizsich levelu k vyssim.
Vyuzivame incremental QBF solving?

@@

  \caption{An example illustrating the results of the three basic
    reduction levels: an input automaton and the automata
    obtained by reduction of level 1, level 2, and level 3.
    \todo{Pozor, prvni klauzule v levelu 2 je trash!}}
  \label{fig:example}
\end{figure}
%}}}
%{{{ algorithm and implementation

\section{Reduction algorithm and its implementation}\label{sec:algimpl}

@@

Jak se nastavuji inicialni parametry a jak postupne klesaji.
Jak prechazim od nizsich levelu k vyssim.
Vyuzivame incremental QBF solving?

>>>>

\paragraph*{Structure of the paper} The next section introduces basic
terms used in the paper. Section~\ref{sec:qbf} explains the
construction of three mentioned QBF formulas. The reduction algorithm
based on these formulas is presented in
Section~\ref{sec:algo}. Section~\ref{sec:implementation} describes our
tool \telatko implemening the reduction technique.
Experimental results are shown in
Section~\ref{sec:experiments}. Finally, Section~\ref{sec:conclusion}
suggests other applications of our QBF-based reduction technique and
closes the paper.

@@

%}}}
%{{{ algorithm

\section{Reduction algorithm}\label{sec:algo}
Jak se nastavuji inicialni parametry a jak postupne klesaji.
Jak prechazim od nizsich levelu k vyssim.
Vyuzivame incremental QBF solving?

@@

  \caption{An example illustrating the results of the three basic
    reduction levels: an input automaton and the automata
    obtained by reduction of level 1, level 2, and level 3.
    \todo{Pozor, prvni klauzule v levelu 2 je trash!}}
  \label{fig:example}
\end{figure}

%}}}
%{{{ implementation

\section{Implementation}\label{sec:implementation}

@@

\todo{Jake parametry ten tool ma? Co potrebuje k behu? Kde je dostupny? Pod jakou licenci?}
